### 2025-05-20 PaperSections.Rmd
Updated sample size table.

```
## - Figure 2
```{r, fig.width=5, fig.height=5}
load("./Data/nlbasemap.RData")

@@

>>>>

```
## - Figure 1
```{r, fig.width=5, fig.height=5}
load("./Data/nlbasemap.RData")

@@

# Sample size

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SE-1995.RData")

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)
Eaps1 <- AP_stos %>% filter(length > 29)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)

### Fall
```{r}
load(file = "./ModelSaves/Set_Up/FE-1994.RData")

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)
Eapf1 <- AP_stof %>% filter(length > 29)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1988)
Eghf0 <- GH_stof %>% filter(length < 20)
Eapf0 <- AP_stof %>% filter(length < 30)

### Total
```{r}
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SC-2019.RData")

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)

### Fall
```{r}
# load rstrap set data
load(file = "./ModelSaves/Set_Up/FC-2020.RData")

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Cghf0 <- GH_stof %>% filter(length < 20)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)

### Total
```{r}

Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")
Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")
Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")

## All data
```{r}
# Combine seasonal data for
## Engel
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")

Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")

Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

## Campelen
Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")

Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")

Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")

# Combine species data from the Engel and Campelen timeseries
Tac0 <- rbind(Eac0, Cac0)
Tac1 <- rbind(Eac1, Cac1)
Tac2 <- rbind(Eac2, Cac2)

Tap0 <- rbind(Eap0, Cap0)
Tap1 <- rbind(Eap1, Cap1)

Tgh0 <- rbind(Egh0, Cgh0)
Tgh1 <- rbind(Egh1, Cgh1)
Tgh2 <- rbind(Egh2, Cgh2)

## - Table 1
```{r}

sample_size <- data.frame(
  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
  E.pcapelin =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
                  nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
                  nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
                  nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
                  nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
                  nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
                  nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
                  nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),
  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & empty == TRUE))/nrow(filter(Tac0, geartype == "engel"))*100,
                nrow(filter(Tac1, geartype == "engel" & empty == TRUE))/nrow(filter(Tac1, geartype == "engel"))*100,
                nrow(filter(Tac2, geartype == "engel" & empty == TRUE))/nrow(filter(Tac2, geartype == "engel"))*100,
                nrow(filter(Tgh0, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh0, geartype == "engel"))*100,
                nrow(filter(Tgh1, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh1, geartype == "engel"))*100,
                nrow(filter(Tgh2, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh2, geartype == "engel"))*100,
                nrow(filter(Tap0, geartype == "engel" & empty == TRUE))/nrow(filter(Tap0, geartype == "engel"))*100,
                nrow(filter(Tap1, geartype == "engel" & empty == TRUE))/nrow(filter(Tap1, geartype == "engel"))*100),

  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
  C.pcapelin =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
                  nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
                  nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
                  nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                  nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                  nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                  nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
                  nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100),
  C.pempty = c(nrow(filter(Tac0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac0, geartype == "campelen"))*100,
                nrow(filter(Tac1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac1, geartype == "campelen"))*100,
                nrow(filter(Tac2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac2, geartype == "campelen"))*100,
                nrow(filter(Tgh0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                nrow(filter(Tgh1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                nrow(filter(Tgh2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                nrow(filter(Tap0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap0, geartype == "campelen"))*100,
                nrow(filter(Tap1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap1, geartype == "campelen"))*100)

)

sample_size <- sample_size %>% mutate(E.pcapelin = format(E.pcapelin, digits = 4), C.pcapelin = format(C.pcapelin, digits = 4),
                                      E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Figures/samplesize.csv")
